Supplementary file 2

### 2019-08-22 TCGA_E9-A1N5_article.Rmd
article files

---
title: "article_supplementary"
author: "Selcen Ari"
date: "20 Mart 2019"
output:
  pdf_document: default
  html_document: default
bibliography: ref.bib
---

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# Install the packages which is necessary to obtain and process datasets.
#BiocManager::install("SummarizedExperiment", version = "3.8")
library(TCGAbiolinks)
library(SummarizedExperiment)
#install devtools
devtools::install.github(selcenari/ceRNAnetsim)
library(ceRNAnetsim)
```

@@

The methods about miRNA:target interactions are based a basic principle that is reading after isolation of miRNA:target chimerics. The datasets contain all the chimeric miRNA:target structures found in the environment during the experiment. On the other hand, it could be said that the reading is performed as snapshot.Because of that, the methods can provide different chimeric interactions the same miRNA:target pair. We have preferred to select most effective interaction parameters for the same miRNA:target pairs that can exhibit various interactions. The step is performed as:

@@

We have compared two datasets that are obtained for the tumor and normal tissue samples of same patient. We tried to change expression of a gene in normal tissue as the same level in the tumor tissue. Of course, we do not know that the selected gene is responsible for all regulations in the interactions. Moreover, we do not think that one gene causes different regulations in whole interactions. But we wanted to show that a single gene can cause changing regulations of interaction of whole miRNA target network.

@@

```{r}
as.data.frame(E9GE_mirnagenenormal)%>%
iteration_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect, "ABCC1", .iter =200 , how = 4.10, limit = 1)

@@

```{r}
find_iteration(as.data.frame(E9GE_mirnagenenormal), GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect, "ABCC1", .iter =100 , how = 4.10, limit = 10)

@@

as.data.frame(E9GE_mirnagenenormal)%>%
  priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
  update_nodes(once=TRUE)%>%
  update_how("ABCC1", 4.10)%>%
  update_nodes()%>%
  simulate(26)

>>>>

---
title: "Supplementary file 2"
author: "Selcen Ari"
date: "20 Mart 2019"
output:
  pdf_document: default
  html_document: default
bibliography: ref.bib
---

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# Install the packages which is necessary to obtain and process datasets.
#install.packages("BiocManager")
#BiocManager::install("SummarizedExperiment")
#BiocManager::install("TCGAbiolinks")
library(TCGAbiolinks)
library(SummarizedExperiment)
#install devtools
#devtools::install_github("selcenari/ceRNAnetsim")
library(ceRNAnetsim)
```

@@

The methods about miRNA:target interactions are based a basic principle that is reading after isolation of miRNA:target chimerics. The datasets contain all the chimeric miRNA:target structures found in the medium during the experiment. On the other hand, it could be said that the reading is performed as snapshot.Because of that, the methods can provide different chimeric interactions the same miRNA:target pair. We have preferred to select most effective interaction parameters for the same miRNA:target pairs that can exhibit various interactions. The step is performed as:

@@

We have compared two datasets that are obtained for the tumor and normal tissue samples of same patient. We tried to change expression of a gene in normal tissue as the same level in the tumor tissue. Of course, we do not know that the selected gene is responsible for all regulations in the interactions. Moreover, it is not considered that one gene causes different regulations in whole interactions. But we wanted to show that a single gene can cause changing regulations of interaction of whole miRNA target network.

@@

```{r}
as.data.frame(E9GE_mirnagenenormal)%>%
 priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
 update_how("ABCC1",4.10) %>%
 simulate(100) %>%
 find_iteration(limit=0, plot= TRUE)

@@

```{r}
as.data.frame(E9GE_mirnagenenormal)%>%
 priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
 update_how("ABCC1",4.10) %>%
 simulate(100) %>%
 find_iteration(limit=0, plot= FALSE)

@@

as.data.frame(E9GE_mirnagenenormal)%>%
  priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
  update_how("ABCC1", 4.10)%>%
  simulate(26)
